Intervention Bandits

### 2015-01-19 causal-bandit/c-bandit.tex
regret bound for observe until plausible set smaller than alpha

\eqn {
R_n = & \max_{i=1...K} E\left[\sum_{t=1}^n Y_{it} - \sum_{t=1}^n Y_{I_t,t} \right] \\
= & E[n]\left(P(Y|X_{i^*}={j^*})  - P(Y)\right) \text{ where } X_{i^*}={j^*} \text{ is the best arm}
}

If \ref{eq:overlap3} is true, we can bound the probability of overlap  been the confidence intervals of the best arm and one of the other arms, $k$, at some timestep $t$ with the union bound of the probability that either \ref{eq:overlap1} or \ref{eq:overlap2} are false.

Now for random variables $W_{sij} = P(Y|X_i=j)$ drawn from a Bernoulli distribution with mean $p_{ij}$ the Chernoff inequality gives:

\eqn {
& P(\frac{1}{t}\sum_s W_{sij} - p_{ij} \geq \gamma) \leq \exp(-\frac{t\gamma^2}{2p_{ij}(1-p_{ij})+2\gamma/3}) \\
\implies & P(\frac{1}{t}\sum_s \frac{W_{sij}}{p} - \frac{p_{ij}}{p} \geq \epsilon) = P(\hat{\mu}_i - \mu_i \geq \epsilon) \leq \exp(-\frac{tp\epsilon^2}{2+2\epsilon/3}) = \exp(-\frac{t\epsilon^2}{4+4\epsilon/3})
}
Where $p_{ij} = P(Y = 1, X_i = j) \leq P(X_i=j) = p = 1/2 \;\;\; \forall(i,j)$

Similarly

\eqn {
P(\mu^* - \hat{\mu}^* \geq \epsilon) \leq exp(-tp^2\epsilon^2) = exp(-\frac{t\epsilon^2}{4})
}

\eqn {
E[n] = \sum_{t=1}^\infty P(n \geq t) \leq & \sum_{t=1}^\infty \left( \exp(-\frac{t\epsilon^2}{4+4\epsilon/3}) +exp(-\frac{t\epsilon^2}{4}) \right) \\
= & \frac{1}{\exp(\epsilon^2/(4+4\epsilon/3)) - 1} + \frac{1}{\exp(\epsilon^2/4) - 1} \\
\leq & \frac{2}{\exp(\epsilon^2/(4+4\epsilon/3)) - 1} \\
= & \frac{2}{\exp(a^2/(64+4a/3)) - 1}
}

@@

>>>>

Let $n$ be the number of timesteps until the size of the set $A_t$ falls below $\alpha$ or we reach the overall horizon $T$

\eqn {
n = \min(\{t:size(A_t)< \alpha, T\})
}

Let $Q(k)$ be the expected reward for arm $k$ and $\mu^*$ be the expected reward for the best arm.

\eqn {
R_n = & \max_{i=1...K} E\left[\sum_{t=1}^n Y_{it} - \sum_{t=1}^n Y_{I_t,t} \right] \\
= & E[n]\left(\mu^*  - E[Q]\right) 
}

Without loss of generality, assume the arms are ordered from best to worst.

\eqn{
& Q(k = 1...K) = [\mu^*, \mu^*-d_2 ... \mu^*-d_k] \\
&\implies E[Q] = \mu^* - \frac{1}{K}\sum_{k=2}^K d_k \\
&\implies  R_n = E[n]\left(\frac{1}{K}\sum_{k=2}^K d_k \right)
}

Whenever the following two statements hold only arms with indexes less than $\alpha$ can be in the set $A_t$:

\eqn {
& \mu^* - \hat{\mu}^* \leq \frac{d_\alpha}{2} \\
& \hat{\mu_k} - \mu_k \leq \frac{d_k}{2} \; \forall k \geq \alpha 
}

\eqn{
\label{eq:proboverlap}
\implies \rho(t) \equiv P(\exists k \in A_t: k \geq \alpha)  \leq P(\mu^* - \hat{\mu}^* > \frac{d_\alpha}{2}) + \sum_{k=\alpha}^K P( \hat{\mu_k} - \mu_k > \frac{d_k}{2})
}

\eqn {
P(n > t) = \begin{cases} 0 & \text{if } t \geq T \\
P(\exists k \in A_t: k \geq \alpha) & \text{otherwise}
\end{cases}
}

We now concentrate bounding \ref{eq:proboverlap}. For random variables $W_{sij} = P(Y|X_i=j)$ drawn from a Bernoulli distribution with mean $p_{ij}$ the Chernoff inequality gives:

\eqn {
& P(\frac{1}{t}\sum_s W_{sij} - p_{ij} \geq \gamma) \leq \exp(-\frac{t\gamma^2}{2p_{ij}(1-p_{ij})+2\gamma/3}) \\
\implies & P(\frac{1}{t}\sum_s \frac{W_{sij}}{p} - \frac{p_{ij}}{p} \geq \epsilon) = P(\hat{\mu}_k - \mu_k \geq \epsilon) \leq \exp(-\frac{tp\epsilon^2}{2+2\epsilon/3}) = \exp(-\frac{t\epsilon^2}{4+4\epsilon/3})
}
Where $p_{ij} = P(Y = 1, X_i = j) \leq P(X_i=j) = p = 1/2 \;\;\; \forall(i,j)$

Similarly, 
\eqn {
P(\mu^* - \hat{\mu}^* \geq \epsilon) \leq exp(-tp^2\epsilon^2) = exp(-\frac{t\epsilon^2}{4})
}

\eqn {
\implies \rho(t) \leq \exp(-\frac{ d_\alpha^2 t}{16}) + \sum_{k=\alpha}^K exp(-\frac{d_k^2 t}{16(1+d_k/6)})
}

\eqn{ 
E[n] = & \sum_{t=1}^T P(n \geq t) \leq \sum_{t=1}^T \rho(t) \\
= & \min \left(T, \frac{1 - e^{-d_\alpha^2 T/16}}{e^{d_\alpha^2 /16} -1 } +  \sum_{k=\alpha}^K \frac{1 - e^{-d_k^2 T/16(1+d_k/6)}}{e^{d_k^2 /16(1+d_k/6)} -1 } \right)
}

Since the regret is $R_n = E[n]\left(\frac{1}{K}\sum_{k=2}^K d_k \right)$ the worst case is that just enough of the differences $d_k$ are $0$ to make $E[n] = T$ and the remainder are $1$. This occurs if $d_\alpha = 0$, In this case the regret is:

\eqn {
R_n = T \left(\frac{K-(\alpha+1)}{K}\right)
}

@@

\eqn {
E[n] = \sum_{t=1}^T P(n \geq t) \leq & \sum_{t=1}^\infty \left( \exp(-\frac{t\epsilon^2}{4+4\epsilon/3}) +exp(-\frac{t\epsilon^2}{4}) \right) \\
= & \frac{1}{\exp(\epsilon^2/(4+4\epsilon/3)) - 1} + \frac{1}{\exp(\epsilon^2/4) - 1} \\
\leq & \frac{2}{\exp(\epsilon^2/(4+4\epsilon/3)) - 1} \\
= & \frac{2}{\exp(a^2/(64+4a/3)) - 1}
}

If \ref{eq:overlap3} is true, we can bound the probability of overlap  been the confidence intervals of the best arm and one of the other arms, $k$, at some timestep $t$ with the union bound of the probability that either \ref{eq:overlap1} or \ref{eq:overlap2} are false FOR ALL ARMS.
